DATA 621 Homework #4

### 2019-11-15 hw4/HW4.Rmd
More work

```{r}
M <- amt_train %>%
  select(-INDEX) %>%
  keep(is.numeric) %>%
  cor(.)
corrplot(M, type = "upper")

```

@@

The challenge will be to create a classifier.  Let's explore the correlations to see what is correlated:

```{r, null_prefix = TRUE}
amt_train %>%
  keep(is.numeric)%>%
  select(-TARGET_AMT_OUTLIER, -INDEX) %>%
  cor(., amt_train$TARGET_AMT_OUTLIER)

```

>>>>

```{r}
M <- amt_train %>%
  select(-INDEX) %>%
  keep(is.numeric) %>%
  cor(.)
corrplot(M, type = "upper")
```

```{r}
amt_train %>%
  keep(is.numeric)%>%
  select(-INDEX, -TARGET_AMT) %>%
  cor(., amt_train$TARGET_AMT) %>%
  kable() %>%
  kable_styling()
```

@@

The challenge will be to create a classifier.  There are `r nrow(amt_train[amt_train$TARGET_AMT_OUTLIER == 1,])` out of `r nrow(amt_train)` that are outliers.  Let's create another balanced data set and see if we can build a classifier.

```{r}
set.seed(42)
minority <- nrow(amt_train[amt_train$TARGET_AMT_OUTLIER == 1,])
majority <- nrow(amt_train[amt_train$TARGET_AMT_OUTLIER == 0,])
diff <- majority - minority
minority_index <- amt_train[amt_train$TARGET_AMT_OUTLIER == 1,]$INDEX
over_sample_train_2 <- data.frame(INDEX = sample(minority_index, diff, TRUE)) %>%
  merge(amt_train, .) %>%
  bind_rows(amt_train)
```

Let's explore the correlations to see what is correlated:

```{r}
over_sample_train_2 %>%
  keep(is.numeric)%>%
  select(-TARGET_AMT_OUTLIER, -INDEX, -TARGET_AMT) %>%
  cor(., over_sample_train_2$TARGET_AMT_OUTLIER) %>%
  kable() %>%
  kable_styling()
```

```{r}
M <- over_sample_train_2 %>%
  select(-INDEX, -TARGET_AMT) %>%
  keep(is.numeric) %>%
  cor(.)
corrplot(M, type = "upper")
```
